---
title: "h8"
author: "grienne"
date: "November 1, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Base}

library(ggplot2)
library(dplyr)
require(ggmosaic)                       #<-- for mosaic plots
require(epitools) 

dat <- read.table(file = "grad_dat.txt", header = T)
attach(dat)

```


1. Build a logistic model to predict the chances of graduation given family income.
Construct 95% confidence intervals for model parameters. Do they capture the true
values of β0 and β1 that you calculate in Assignment #7 (1)?

      Homework 7 Question: 1
          Bo = -.99 
          B1 =  .497
      Yes, they are captured.
            
```{r Question 1}

q1_glm <- glm(grad.flg ~ income, family = binomial(link = 'logit'))

summary(q1_glm)
confint(q1_glm)
exp(confint(q1_glm))
exp(-.99) 
exp(.497)

```


2. Comparing logit and probit: fit this data using the probit model:
glm(grad.flg ~ income, data = dat, family = binomial(link = 'probit'))


```{r Question 2}

q2_glm <- glm(grad.flg ~ income, data = dat, family = binomial(link = 'probit'))
summary(q2_glm)

q1_glm_scale <- coef(q1_glm)
q1_glm_scale / 1.6

```

3. Using the latent variable formulation, find the cut point in income after which a
student is more likely to graduate than not. Plot the fitted values from your logistic
regression with a vertical line showing the estimated cut point in income.


```{r Question 3}
mean_ng <- coefficients(q1_glm) %*% c(1, 0)
mean_g <- coefficients(q1_glm) %*% c(1, 1)

zi <- seq(-4, 6, 0.01)
tmp.dat <- data.frame(x = zi, f = dlogis(zi, mean_ng, 1), m = dlogis(zi, mean_g, 1))

p = ggplot(tmp.dat)
p + geom_line(aes(x = x, y = f), colour = 'red') +
    geom_line(aes(x = x, y = m), color = 'blue') +
    geom_vline(xintercept = c(0)) +
    geom_hline(yintercept = c(0), linetype = 'dashed') +
    geom_ribbon(data = subset(tmp.dat, x < 0), aes(x = x, ymax = m),
                ymin = 0, fill = "blue", alpha = 0.3) +
    geom_ribbon(data = subset(tmp.dat, x < 0), aes(x = x, ymax = f),
                ymin = 0, fill = "red", alpha = 0.5) +
    scale_x_continuous("Latent variable Z") +
    scale_y_continuous("Probability Density Function of Z") +
    theme_bw() +
    theme(axis.text=element_text(size=rel(1.9)),
          axis.text.x=element_text(vjust=0),
          axis.title.x=element_text(colour="grey10",vjust=0,size=rel(2)),
          axis.title.y=element_text(colour="red",size=rel(2),vjust=0.3),
          plot.title = element_text(colour="grey10",size=rel(2)))

######

##predicted values
dat$final.probs <- predict(q1_glm, type = 'response')

cut.g <- - q1_glm$coefficients[1] / q1_glm$coefficients[2]
sigma.g <- 1 / q1_glm$coefficients[2]

#cut.g <- - (q1_glm$coefficients[1] + q1_glm$coefficients[3]) / (q1_glm$coefficients[2] + q1_glm$coefficients[4])
#sigma.g <- 1 / (q1_glm$coefficients[2] + q1_glm$coefficients[4])

    
p  = ggplot(dat)
p + #geom_line(aes(x = income, y = I(expected(income, cut.ng, sigma.ng))), colour = 'red')+
    geom_line(aes(x = income, y = final.probs, colour = 'blue'))+
    geom_point(aes(x = income, y = grad.flg), size = 5, alpha = 0.1) +
    annotate("text", label="cut.point = 12,900", x=2, y=.5, size=3) +
    #geom_segment(aes(x = cut.ng, y = 0, xend = cut.ng, yend = 1), colour = 'red') +
    geom_segment(aes(x = cut.g, y = 0, xend = cut.g, yend = 1), colour = 'blue') +
    scale_y_continuous("Pr(Graduation)", limits = c(0,1)) +
    scale_x_continuous("Income") +
    geom_hline(yintercept = c(0, 1), linetype = 'dashed') +
    theme_bw() +
    theme(axis.text=element_text(size=rel(1.9)),
          axis.text.x=element_text(vjust=0),
          axis.title.x=element_text(colour="grey10",vjust=0,size=rel(2)),
          axis.title.y=element_text(colour="red",size=rel(2),vjust=0.3),
          plot.title = element_text(colour="grey10",size=rel(2)))





```

